The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
remove some finished conversations

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{axis_ratio_odod}
 %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
 %b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
 %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
 %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
 \caption{Galaxy axis ratio
   distributions in two overdense redshift bins, $z=0.65-0.75$ (blue) and
   $z=0.80-0.85$ (red), to check for consistency in the case that the
   environment is the same even if the redshift differs. The
   $p$-values from the KS and AD tests are given in
   Table.~\ref{table:pvalues_all}. \rachel{Figure does not appear to
     be centered.}\arun{Fixed.}}
 \label{fig:axisratio_similar}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{axis_ratio_odud}
 %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
 %#b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
 %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
 %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
 \caption{Galaxy axis ratio distributions in a single underdense redshift
   slice, $z=0.55-0.65$ (blue), and a single overdense redshift slice,
   $z=0.65-0.75$ (red). The $p$-values from the
   KS and AD tests are given in Table.~\ref{table:pvalues_all}.   \rachel{Figure does not appear to
     be centered.}\arun{Fixed.}}
 \label{fig:axisratio_contrasting}
\end{figure*}

@@

\rachel{Overall, I find it quite confusing that the underdense regions
  are red and the overdense regions are blue on all of the plots in
  this section and the section on \sersic $n$ and $B/T$.
  The underdense regions are dominated by blue galaxies and the
  overdense are dominated by red galaxies, so having the plot colors
  reversed creates some cognitive dissonance.  Can you reverse them to
  more naturally match up point color with galaxy type?} \arun{Fixed.}

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{axis_ratio_odod}
 %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot65-0dot75.eps} \
 %b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot80-0dot85.eps} \\
 %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot80-0dot85.eps} \
 %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot75-0dot8.eps} \
 \caption{Galaxy axis ratio
   distributions in two overdense redshift bins, $z=0.65-0.75$ (blue) and
   $z=0.80-0.85$ (red), to check for consistency in the case that the
   environment is the same even if the redshift differs. The
   $p$-values from the KS and AD tests are given in
   Table.~\ref{table:pvalues_all}.}
 \label{fig:axisratio_similar}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{axis_ratio_odud}
 %a) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot55-0dot65_0dot65-0dot75.eps} \
 %#b) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot55-0dot65.eps} \\
 %c) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot3-0dot4_0dot75-0dot8.eps} \
 %d) \includegraphics[width=0.9\columnwidth]{axisratio(0)_0dot65-0dot75_0dot75-0dot80.eps} \
 \caption{Galaxy axis ratio distributions in a single underdense redshift
   slice, $z=0.55-0.65$ (blue), and a single overdense redshift slice,
   $z=0.65-0.75$ (red). The $p$-values from the
   KS and AD tests are given in Table.~\ref{table:pvalues_all}. }
 \label{fig:axisratio_contrasting}
\end{figure*}

@@
